### 2024-04-05 doc/15yrsChange.Rmd
acknowledgements and author contributions

- Funding: ForestGEO

@@

LLM, RMH, KJB, IAK, EM, CT, JS, KAT, WJM and NAB conceived the ideas and designed methodology; RMH, KJB, IAK, EM, CT, CP, EGA, JJ, JS and LM collected the data; LLM, RH, KJB, IAK, EM and VH analyzed the data; LLM and RMH led the writing of the manuscript. All authors contributed critically to the drafts and gave final approval for publication.

>>>>

We gratefully acknowledge the many researchers who have collected data at the SCBI ForestGEO plot over the years. 
This research was funded by Smithsonian's Forest Global Earth Observatory, Smithsonian's National Zoo and Conservation Biology Institute, NSF Macrosystems grant #2106015, and grants from Virginia Native Plants Society<!--2017 and 2019 mortality censuses--> and Shenandoah National Park Trust<!--2018 mortality census-->.

@@

LLM, RMH, KJB, IAK, EM, CT, DM, JS, NAB, WJM, and KAT conceived the ideas and designed methodology; all researchers contributed to data collection; LLM, RH, KJB, IAK, EM and VH analyzed the data; LLM and RMH led the writing of the manuscript. All authors contributed critically to the drafts and gave final approval for publication.
